
% definitions and configuration

\font\fnname=cmbx10 at 17pt
\font\fnsection=cmbx10 at 14pt
\font\fnsmall=cmr9
\font\fnlabel=cmbx10

\def\tinyskip{\vskip 0.2in}
\def\miniskip{\vskip 0.1in}
\def\microskip{\vskip 0.05in}

\def\sectionhead#1{\tinyskip\noindent{\fnsection #1}\miniskip}

\def\accomplish#1{\parindent=5pt$\bullet$ \hbox{\hsize=35pc \vtop{\noindent #1}} \microskip}
%\def\accomplish#1{\leftskip=10pt\parindent=-10pt$\bullet$ #1 \microskip\leftskip=0pt}
%\def\accomplish#1{\parindent=10pt\item{$\bullet$}#1 \microskip}

\def\skill#1#2{\noindent{\fnlabel #1} #2\microskip}

\def\employer#1#2{\noindent{\fnlabel#1}\hfil\break#2\microskip}

\headline={
  \ifnum\pageno=1
    \hfill
  \else
    Bruce A King\hfill\folio
  \fi}
\nopagenumbers

% Let it begin

\centerline{\fnname Bruce A King}
\centerline{\fnsmall Eugene Oregon}
\centerline{\fnsmall (541) 513 -- 6698}
\centerline{\fnsmall bruce@minuteproductions.com}
\centerline{\fnsmall https://github.com/brucealon/}

\sectionhead{Professional Summary}

\noindent
Senior Software Engineer with over 20 years of professional experience
developing reliable, useful applications and helping customers and
coworkers to meet their needs. I am an avid autodidact with a wide
range of interests.

\sectionhead{Skills}

\skill
  {Containers} {Experienced deploying applications with Docker and
  Kubernetes.}

\skill
  {Databases} {Strong SQL skills. Familiar with NoSQL. Experienced
  with data transfer formats like JSON, XML, and YAML as well as
  simpler comma- and tab-delimited files.}

\skill
  {Networks} {Experienced in TCP/IP networking concepts and
  applications.}

\skill
  {Operating Systems} {Administering and troubleshooting Linux (rpm,
  dnf, yum, apt-get, apk), OS X, and Microsoft Windows.}

\skill
  {Programming Languages} {Experienced with BASH, C/C++, Emacs Lisp,
  Groovy, Java, JavaScript, Perl, PHP, PL/SQL, Python, Ruby, and
  Windows PowerShell. Some familiarity with Clojure, Elixir, Erlang,
  Haskell, and PostScript. Experienced with imperative and
  Object-Oriented programming. Familiar with functional programming.}

\skill
  {Systems Administration} {Extensive experience using and
  administering Linux, Unix, and Windows systems, including a variety
  of services (daemons).}

\skill
  {Tools} {Experienced with a variety of command-line tools for
  version control (git, subversion, cvs), virtualization (vagrant,
  docker, kubectl), content examination and exploration (grep, awk,
  sed, xmlstarlet, jq), and many other tasks. Experienced with a
  number of graphical tools such as SoapUI and Postman; SQL Server
  Integration Services to link data from SQL Server to external
  third-party systems; and SQL Server Reporting Services.}

\skill
  {Virtualization} {Familiar with using VMware, VirtualBox, Vagrant
  and other virtualization technologies for testing and
  troubleshooting and for standardized development environments.}

\skill
  {Web Development} {Fluent in developing Internet and intranet
  scripts and applications in C, Perl, Java, HTML, CSS, and
  JavaScript.}

\sectionhead{Employment}

\employer
  {Symantec --- Springfield, OR}
  {Principle Software Engineer, 2016--Present}

\accomplish {Contributed features and bug fixes to the consumer support web site, built in Java/Spring,
supporting an average of 200,000 daily users worldwide with over two
dozen country/language localizations, coordinating many phone and chat
support partners and vendors, and available in multiple layouts
including responsive/mobile and right-to-left languages.}

\accomplish{Led the migration of the consumer support web site and other
applications from IT-managed on premises infrastructure to team managed
Kubernetes clusters in Microsoft Azure.}

\accomplish{Trained other members of my team in the use and management of
Docker and Kubernetes via YAML configuration files and command
line tools.}

\accomplish{Supported and extended multiple REST APIs running on
Ruby/Sinatra.}

\accomplish{Supported an internal Jenkins CI/CD application relied on by
several teams. This is running in a Docker container in
Kubernetes, which provided some interesting challenges and is not,
perhaps, the recommended configuration for Jenkins, but
maintaining it was essential to migrating to Kubernetes in a
reasonable timeframe with minimal disruption, a goal we achieved.}

\miniskip
\employer
  {Eugene School District 4J --- Eugene, OR}
  {Senior Application Developer, 2011--2016}

\accomplish{Converted student-oriented data for a roughly 16,000 student
school district from the discontinued AAL product eSIS, running on
Linux and Oracle, to Edupoint's Synergy running on Microsoft
Windows Server 2008 and Microsoft SQL Server 2008 R2.}

\accomplish{Collaborated with school administrators to develop the Early
Warning System report, a tool to identify, based on attendance and
failing grades, High School students who need additional help.}

\accomplish{Collaborated with school administrators and student counselors
to develop the Graduation Requirements Report, used both to
determine what each student still needs to accomplish in order to
graduate and, longitudinally, to track performance from school to
school and across the district. The graduation requirements
information had been available only for individual students and
could take up to 30 seconds per student to load. The Graduation
Requirements Report combined that data with additional
demographics and exported all students for a school or even the
entire district to Excel for later sorting and other
manipulations.}

\accomplish{Built and/or maintained a number of processes to extract data
from the Student Information System for import into third-party
systems such as Naviance, a college and career readiness platform,
and Follett Destiny, a Library Management System, as well as
several others. The extracts were developed in BASH, Perl,
PowerShell, SQL Server Integration Services, and other languages
and tools, and spread across a number of Linux and Windows
systems, executing from within Oracle or SQL Server or from cron
jobs and other configurations.}

\accomplish{For the new Student Information System I worked to standardize
all third-party integrations into SSIS packages and PowerShell
scripts, with a small number of Perl scripts, all running on one
system managed through SQL Server Management Studio to reduce the
confusion and documentation involved in routine modifications and
in troubleshooting problems.}

\accomplish{Wrote processes to import student assessments into
Synergy. The handled assessments include ACT, AP, easyCBM,
EXPLORE, OAKS, PLAN, PSAT, SAT, SBAC, and Work Keys with a system
that is simple to modify so that as new assessments are
implemented in the district they can easily be imported into the
Student Information System.}

\accomplish{Wrote often complicated SQL on a daily basis to investigate
questions and troubleshoot problems, at all times striving to
improve both accuracy and efficiency.}

\miniskip
\employer
  {Symantec --- Springfield, OR}
  {Software Engineer, 2005--2011}

\accomplish{Served as the primary contact for all UNIX server issues and
helped IT troubleshoot and solve various problems involving httpd
servers and application containers as well as network connectivity
problems, permissions issues, symbolic links, etc.}

\accomplish{Architecture lead responsible for investigating, implementing,
and teaching new methods and frameworks, such as unit testing and
test driven development.}

\accomplish{Took over the lead maintainer role for Monarch, a Flex MVC
framework derived from Cairngorm, used in our award winning
One-Click Support project for the Norton line of consumer
products.}

\accomplish{Learned Ruby and took over maintenance of a Ruby project that
consolidated XML data files into a compressed Action Message
Format (AMF) file that reduced load times for a Flex consumer
support application.}

\accomplish{Primary server administrator for our internal system,
installing, configuring, and maintaining PostgreSQL and MySQL
RDBMSs, Apache httpd, BEA Weblogic and Apache Tomcat application
servers, user accounts, and various individual needs.}

\accomplish{Lead developer for Common Error Dialog, an error to solution
linking system, written in Java, that, by connecting consumer
product customers to step-by-step instructions, helped them solve
their problems without having to contact our support departments,
thereby substantially reducing Symantec's support costs.}

\miniskip
\employer
  {ViewTouch --- Eugene, OR}
  {Developer, 2002--2005}

\accomplish{Developed Point-of-Sales software for the X Windows platform
on FreeBSD and Linux, written in C/C++.}

\accomplish{Designed and developed supporting utilities for installation,
data backup and recovery, background report generation, and other
tasks.}

\accomplish{Interfaced with other companies to implement credit card
features using multiple APIs and processors.}

\miniskip
\employer
  {Symantec --- Eugene, OR}
  {Web Developer, 1998--2001}

\accomplish{Designed and developed message routing system that
significantly and measurably improved technician efficiency in
handling customer problems.}

\accomplish{Developed a scriptable system (direct.cgi) that allowed the
overseas teams to more quickly generate pages for new products and
versions.}

\accomplish{As part of larger team, designed and developed award-winning
interactive Web pages and scripts to facilitate technical and
customer support operations.}

\sectionhead{Education}

\employer
  {Lane Community College}
  {Eugene, OR}

\accomplish{Focused on networking and programming.}

\bye
